Time series clusters

### 2020-08-10 src/Data_Spatial.Rmd
minor change on comments
knitted descriptive_clusters.Rmd

# drop NAs
TSbb19_20sp <- TSbb19_20sp[!is.na(TSbb19_20sp$LAD19NM),]
#NA LAD19NM, coord outside UK =  615516 obs (99.3% of obs retained)

#save files
out.TSbb19_20sp <- paste(path, "./data/temp/TSbb19_20sp.csv", sep = "")
write_csv(TSbb19_20sp, out.TSbb19_20sp)
```

>>>>

# drop NAs
TSbb19_20sp <- TSbb19_20sp[!is.na(TSbb19_20sp$LAD19NM),]
#NA LAD19NM, coord outside UK =  2618 / 405568 obs (99.4% of obs retained)

#save files
out.TSbb19_20sp <- paste(path, "/data/temp/TSbb19_20sp.csv", sep = "")
write_csv(TSbb19_20sp, out.TSbb19_20sp)
```

### 2020-08-10 src/ts_clusters.Rmd
knitted descriptive_clusters.Rmd

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)

@@

clusters  %>% arrange(cluster.up) %>% kable()

@@

#la@data <- merge(la@data, clusters, by.x = "LAD19NM", by.y = "LAD")
la@data <- merge(la@data, clusters, by.x = "lad19nm", by.y = "LAD")

# plot maps
# var <- la@data[ ,'cluster.up']
# plot(la, col = var, main = "Upload clusters",
#      border = rgb(0.8, 0.8, 0.8, 0))
# 
# var <- la@data[ ,'cluster.up.diff']
# plot(la, col = var, main = "Upload difference clusters",
#      border = rgb(0.8, 0.8, 0.8, 0))
# 
# 
# var <- la@data[ ,'cluster.down']
# plot(la, col = var, main = "Download clusters",
#      border = rgb(0.8, 0.8, 0.8, 0))
# 
# var <- la@data[ ,'cluster.tests']
# plot(la, col = var, main = "Tests clusters",
#      border = rgb(0.8, 0.8, 0.8, 0))

# leaflet maps

# factors
la@data$cluster.up <- as.factor(la@data$cluster.up)
la@data$cluster.down <- as.factor(la@data$cluster.down)
la@data$cluster.up.diff <- as.factor(la@data$cluster.up.diff)
la@data$cluster.down.diff <- as.factor(la@data$cluster.down.diff)
la@data$cluster.tests <- as.factor(la@data$cluster.tests)

# palettes
factpal.up <- colorFactor("RdYlBu", la@data$cluster.up)
factpal.down <- colorFactor("RdYlBu", la@data$cluster.down)
factpal.up.diff <- colorFactor("RdYlBu", la@data$cluster.up.diff)
factpal.down.diff <- colorFactor("RdYlBu", la@data$cluster.down.diff)
factpal.tests <- colorFactor("RdYlBu", la@data$cluster.tests)

leaflet(la) %>%
  # add polygons as groups
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.up(cluster.up), group = "cluster.up") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.down(cluster.down), group = "cluster.down") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.up.diff(cluster.up.diff), group = "cluster.up.diff") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.down.diff(cluster.down.diff), group = "cluster.down.diff") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.tests(cluster.tests), group = "cluster.tests") %>%
  # hide groups, so they don't appear all on in the begining 
  hideGroup("cluster.up") %>%
  hideGroup("cluster.down") %>%
  hideGroup("cluster.up.diff") %>%
  hideGroup("cluster.down.diff") %>%
  hideGroup("cluster.tests") %>%
  # layer control
  addLayersControl(
    #baseGroups = c("Upload)", "Download"),
    overlayGroups = c("cluster.up","cluster.down", "cluster.down", "cluster.up.diff", "cluster.down.diff", "cluster.tests"),
    options = layersControlOptions(collapsed = FALSE)) %>%
  # add different legends
  addLegend(pal = factpal.up, 
            values = la@data$cluster.up,
            opacity = 1,
            group = "cluster.up",
            title = "Upload clusters") %>%
  addLegend(pal = factpal.down, 
            values = la@data$cluster.down,
            opacity = 1,
            group = "cluster.down",
            title = "Download clusters") %>%
  addLegend(pal = factpal.up.diff, 
            values = la@data$cluster.up.diff,
            opacity = 1,
            group = "cluster.up.diff",
            title = "Upload diff. clusters") %>%
  addLegend(pal = factpal.down.diff, 
            values = la@data$cluster.down.diff,
            opacity = 1,
            group = "cluster.down.diff",
            title = "Download diff. clusters") %>%
  addLegend(pal = factpal.tests, 
            values = la@data$cluster.tests,
            opacity = 1,
            group = "cluster.tests",
            title = "Test clusters")

@@

>>>>

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)
library(ggmap)

@@

# clusters  %>% arrange(cluster.up) %>% kable()

@@

# ggplot2 maps
la.f <- fortify(la, region = "lad19nm")
la.f <- merge(la.f, clusters.nodiff, by.x = "id", by.y = "LAD")
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.tests))) +
  theme_nothing(legend = TRUE) +
  labs(title = "Test clusters") +
  scale_fill_viridis_d()+
  theme_void()

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  theme_nothing(legend = TRUE) +
  labs(title = "Upload clusters") +
  scale_fill_viridis_d()+
  theme_void()

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.down))) +
  theme_nothing(legend = TRUE) +
  labs(title = "Download clusters") +
  scale_fill_viridis_d()+
  theme_void()

@@

```{r, eval=FALSE}
# leaflet maps

# !!!WRONG CATEGORY VISUALISATION!!!

#la@data <- merge(la@data, clusters, by.x = "LAD19NM", by.y = "LAD")
la@data <- merge(la@data, clusters.nodiff, by.x = "lad19nm", by.y = "LAD")

# from handbook
la@data$cluster.tests <- as.factor(la@data$cluster.tests)
factpal <- colorFactor(topo.colors(5), la@data$cluster.tests)

leaflet(la) %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal(la@data$cluster.tests)) %>%
  addMarkers(lng=la$long, lat=la$lat, popup=la@data$lad19nm) %>%
  addLegend(pal = factpal, 
            values = ~la@data$cluster.tests,
            opacity = 1,
            #group = "cluster.tests",
            title = "Test clusters")

leaflet(la) %>%
  addPolygons(
    fillColor = factpal(la$cluster.tests),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7) %>%
  addMarkers(lng=la$long, lat=la$lat, popup=la@data$lad19nm)

# circles
leaflet(la@data) %>%
  addTiles() %>%
  addCircles(lng = ~long, lat = ~lat, weight = 1, 
             radius = 500L, popup = ~lad19nm, color = ~factpal(cluster.tests))

# factors
la@data$cluster.up <- as.factor(la@data$cluster.up)
la@data$cluster.down <- as.factor(la@data$cluster.down)
#la@data$cluster.up.diff <- as.factor(la@data$cluster.up.diff)
#la@data$cluster.down.diff <- as.factor(la@data$cluster.down.diff)
la@data$cluster.tests <- as.factor(la@data$cluster.tests)

# palettes
factpal.up <- colorFactor("RdYlBu", la@data$cluster.up)
factpal.down <- colorFactor("RdYlBu", la@data$cluster.down)
#factpal.up.diff <- colorFactor("RdYlBu", la@data$cluster.up.diff)
#factpal.down.diff <- colorFactor("RdYlBu", la@data$cluster.down.diff)
factpal.tests <- colorFactor("RdYlBu", la@data$cluster.tests)

leaflet(la) %>%
  # add polygons as groups
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.up(cluster.up), group = "cluster.up") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.down(cluster.down), group = "cluster.down") %>%
  #addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
  #  color = ~factpal.up.diff(cluster.up.diff), group = "cluster.up.diff") %>%
  #addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
  #  color = ~factpal.down.diff(cluster.down.diff), group = "cluster.down.diff") %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~factpal.tests(cluster.tests), group = "cluster.tests") %>%
  addMarkers(lng=la$long, lat=la$lat, popup=la$lad19nm) %>%
  # hide groups, so they don't appear all on in the begining 
  hideGroup("cluster.up") %>%
  hideGroup("cluster.down") %>%
  #hideGroup("cluster.up.diff") %>%
  #hideGroup("cluster.down.diff") %>%
  hideGroup("cluster.tests") %>%
  # layer control
  addLayersControl(
    #baseGroups = c("Upload)", "Download"),
    overlayGroups = c("cluster.up","cluster.down", "cluster.down", "cluster.tests"), #"cluster.up.diff", "cluster.down.diff", 
    options = layersControlOptions(collapsed = FALSE)) %>%
  # add different legends
  addLegend(pal = factpal.up, 
            values = la@data$cluster.up,
            opacity = 1,
            group = "cluster.up",
            title = "Upload clusters") %>%
  addLegend(pal = factpal.down, 
            values = la@data$cluster.down,
            opacity = 1,
            group = "cluster.down",
            title = "Download clusters") %>%
  #addLegend(pal = factpal.up.diff, 
  #          values = la@data$cluster.up.diff,
  #          opacity = 1,
  #          group = "cluster.up.diff",
  #          title = "Upload diff. clusters") %>%
  #addLegend(pal = factpal.down.diff, 
  #          values = la@data$cluster.down.diff,
  #          opacity = 1,
  #          group = "cluster.down.diff",
  #          title = "Download diff. clusters") %>%
  addLegend(pal = factpal.tests, 
            values = la@data$cluster.tests,
            opacity = 1,
            group = "cluster.tests",
            title = "Test clusters")
